≈---
title: "zebra_project"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = FALSE, error = FALSE)
```

## Stripes

```{r, echo = FALSE}
library(tidyverse)
library(ggplot2)
library(ggfortify)
library(pander)
library(knitr)
```

#Methods


```{r}
# Load functions that summarise data - R markdown needs to have these up front befroe the rest of the ode. In an R script, the functions can be at the end.

my_test_ANOVA <- function (df, categorical_name, continuous_name, xlabel, ylabel){
# Function takes a dataframe, and two strings: a categorical variable and a continuous variable. it then does a boxplot and an ANOVA

#Syntax: myresult <- my_test_ANOVA(df, categorical_name, continuous_name, xlabel, ylabel)
# categorical_name and continuous_name are both strings
# Function returns a list with the following items:
#[1] "Figure" = boxplot of the original data
#[2] "Model" = fitted model
#[3] "Autoplot" = autoplot of the original data
#[4] "ANOVA" = ANOVA
#[5] "Coeffs" = coefficients from ANOVA

#After you have called the function, you can access these things e.g.
# myresult[1] - will give you the plot
# myresult[4] - will give you the ANOVA table

# aes_string took me forever to find

# 1. PLOT your data
 myplot <- ggplot(data = df, aes_string(x = categorical_name, y = continuous_name)) +
    geom_boxplot() +
   labs(x = xlabel, y = ylabel)+
   coord_flip()
 
# 2. Fit your model
mymodel <- lm(formula = as.formula(paste(continuous_name,categorical_name,sep="~")), data = df)

# 3. Look at the assumptions
myautoplot <- autoplot(mymodel, smooth.colour = NA)

# 4. Look at the results
myanova <- anova(mymodel)
mytable_of_doom <- summary(mymodel)

# 5. Add interpretation to your graph

# Return list of outputs
newlist <- list("Figure" = myplot, "Model" = mymodel, "Autoplot" = myautoplot, "ANOVA" = myanova, "Coefficients" = mytable_of_doom)
return(newlist)
}


my_test_ANCOVA <- function (df, continuous_response_name, continuous_predictor_name, categorical_name, xlabel, ylabel){
  #Dataset is a dataframe, the names are strings
# aes_string took me forever to find

# 1. PLOT your data
firstplot <- ggplot(data = df) +
  geom_point(aes_string(x = continuous_predictor_name, y = continuous_response_name, color = categorical_name)) +
  labs(x = xlabel, y = ylabel)
 
# 2. Make a model (with an interaction term)
mymodel <- lm(formula = as.formula(paste(continuous_response_name," ~ ",continuous_predictor_name," * ",categorical_name,sep="")), data = df)

# 3. Look at the assumptions
myautoplot <- autoplot(mymodel, smooth.colour = NA)

# 4. Look at the results
myanova <- anova(mymodel)
mytable_of_doom <- summary(mymodel)

# 5. Add interpretation to your graph

max_x = max(subset(df, select = tooth_p1_width))#paste(continuous_predictor_name)))
min_x = min(subset(df, select = tooth_p1_width))#paste(continuous_predictor_name)))

#min_DENSITY = min(subset(limpet, select=DENSITY))

# 100 points to make the CI smooth
# If you just wanted the line then 2 points would be adequate
# expand.grid is a bit like seq but for data frames

newX <- expand.grid(tooth_p1_width = seq(from = min_x, to = max_x, length = 100), sex = c("Male","Female"))
newX

newY <- predict(mymodel, newdata = newX, interval = "confidence", level = 0.95)

addThese <- data.frame(newX, newY)

myplot <- firstplot +
  geom_smooth(data = addThese, aes(ymin = lwr, ymax = upr), stat = "identity")

# Return list of outputs
newlist <- list("Figure" = myplot, "Model" = mymodel, "Autoplot" = myautoplot, "ANOVA" = myanova, "Coeffs" = mytable_of_doom)
return(newlist)
}

```


```{r}
zebra <- read_csv("./data/2017-05-15_zebra-collection-data.csv",
                  col_types = cols(skull_length = col_double(),
                  skull_width = col_double()))

#Burchelli subgroup analysis
burchelli_sg <- zebra %>% filter(species != "Equus_greyvi")

# For each of the continuous variables, does the subspecies make a difference?
t_length_res <- my_test_ANOVA(burchelli_sg, "species", "tooth_p1_length", "Burchelli subspecies", "Length of tooth P1 (mm)")
t_width_res <- my_test_ANOVA(burchelli_sg, "species", "tooth_p1_width", "Burchelli subspecies", "Width of tooth P1 (mm)")
sk_length_res <- my_test_ANOVA(burchelli_sg, "species", "skull_length", "Burchelli subspecies", "Length of skull (mm)")
sk_width_res <- my_test_ANOVA(burchelli_sg, "species", "skull_width", "Burchelli subspecies", "Width of skull (mm)")

# Analysis with dataset omitting subspecies
# Run with subspecies included first

#t_length_pb_t_width_cv_sex_res <- my_test_ANCOVA(burchelli_sg, "tooth_p1_length", "tooth_p1_width", "sex", "Length of tooth P1 (mm)", "Width of tooth P1 (mm)")

df <- burchelli_sg
continuous_predictor_name <- "tooth_p1_length"
continuous_response_name <- "tooth_p1_width"
categorical_name <- "sex"
xlabel <- "Length of tooth P1 (mm)"
ylabel <- "Width of tooth P1 (mm)"


# 1. PLOT your data
firstplot <- ggplot(data = df) +
  geom_point(aes_string(x = continuous_predictor_name, y = continuous_response_name, color = categorical_name)) +
  labs(x = xlabel, y = ylabel)
firstplot
 
# 2. Make a model (with an interaction term)
mymodel <- lm(formula = as.formula(paste(continuous_response_name," ~ ",continuous_predictor_name," * ",categorical_name,sep="")), data = df)

# 3. Look at the assumptions
myautoplot <- autoplot(mymodel, smooth.colour = NA)

# 4. Look at the results
myanova <- anova(mymodel)
mytable_of_doom <- summary(mymodel)

# 5. Add interpretation to your graph

max_x = max(subset(df, select = paste(continuous_predictor_name)))
min_x = min(subset(df, select = paste(continuous_predictor_name)))

# Insert code to find the unique categorical variable options

my_formula1 <- paste(continuous_predictor_name," = seq(from = ",min_x,", to = ",max_x,", length = 100)",sep="")

# Just need to solve the problem of how to get the umique categories then I'm done

unique_categories <- unique(select(df,eval((parse(text = paste(continuous_predictor_name))))))

tbl_df(unique_categories)

my_formula2 <- paste("sex = c(\"Male\",\"Female\")", sep="")

newX <- eval(parse(text = paste("expand.grid(",my_formula1, ", ", my_formula2, ")"))) 
newY <- predict(mymodel, newdata = newX, interval = "confidence", level = 0.95)

addThese <- data.frame(newX, newY)
# Rename the fit column
colnames(addThese)[3] <- continuous_response_name

#Hardwired version to check that data frames are OK
newplot <- firstplot +
  geom_smooth(data = addThese, aes_string(x = continuous_predictor_name, y = continuous_response_name, ymin = "lwr", ymax = "upr", color = categorical_name), stat = "identity")
newplot

# Return list of outputs
newlist <- list("Figure" = firstplot, "Model" = mymodel, "Autoplot" = myautoplot, "ANOVA" = myanova, "Coeffs" = mytable_of_doom)




```

#Results
```{r}
# t_length_pb_t_width_cv_species_res[1]
# t_length_pb_t_width_cv_species_res[3]
# pander(t_length_pb_t_width_cv_species_res[4])
# pander(t_length_pb_t_width_cv_species_res[5])

newlist[1]
newlist[3]
pander(newlist[4])
pander(newlist[5])


```

#Appendix
##1. Does Burchelli subspecies significantly affect the length of tooth P1?

```{r, echo = FALSE}
t_length_res[1]
t_length_res[3]
pander(t_length_res[4])
pander(t_length_res[5])
```

#Appendix
##2. Does Burchelli subspecies significantly affect the width of tooth P1?

```{r, echo = FALSE}
t_width_res[1]
t_width_res[3]
pander(t_width_res[4])
```

#Appendix
##3. Does Burchelli subspecies significantly affect skull length?

```{r, echo = FALSE}
sk_length_res[1]
sk_length_res[3]
pander(sk_length_res[4])
```

#Appendix
##4. Does Burchelli subspecies significantly affect skull width?

```{r, echo = FALSE}
sk_width_res[1]
sk_width_res[3]
pander(sk_width_res[4])
```

```

