---
title: "zebra stats"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

looking for allometry
does tooth area increase at the same rate as skull area

```{r, echo = FALSE}
library(ggplot2)
library(tidyverse)
library(stringr)
library(ggfortify)
library(pander)
library(knitr)
library(broom)
```


```{r, echo = FALSE}
zebra <- read_csv("./data/2017-05-15_zebra-collection-data.csv")
#glimpse(zebra)
```

--------------------------------
plot a graph

```{r}
ggplot(zebra, aes(skull_length , tooth_p1_length)) +
  geom_point(size = 3 , colour = "coral")
```

-----------------------------
making the model

```{r}
model1 <- lm(tooth_p1_length ~ skull_length, data = zebra)
```


checking the assumptions

```{r}
autoplot(model1, smooth.colour = NA)
anova(model1)
summary(model1)
```


yes, skull length does have a significant effect on tooth length p< 0.001, F = 18.174 dF= 25

-----------------------------------
plotting graph looking for allometry

```{r, echo = FALSE}
newX <- expand.grid(skull_length = seq(from = 500, to = 624, length = 100))
#head(newX)


newY <- predict(model1, newdata = newX, interval = "confidence")
#head(newY)


addThese <- data.frame(newX, newY)

addThese <- rename(addThese, tooth_p1_length = fit)

```

plotting the graph with linear regression and confidence limits

```{r, echo = FALSE}
ggplot(zebra, aes(x = skull_length, y = tooth_p1_length)) + 
  geom_point(col = "coral", size = 3) +
  labs(x = "Skull length (mm)", y = "Length of first pre molar (mm)") +
  theme_bw() +
  geom_smooth(data = addThese, aes(ymin = lwr, ymax = upr), stat = "identity")
```


```{r, echo = FALSE}
pander(tidy(model1), justify = c('left','right','right','right','right'), style = 'rmarkdown')

```

In this model, skull length significantly predicts tooth length (p < 0.001).

The model predictions indicate that, in the sample, for every 1 cm increase in skul length, the tooth length increases by 0.5 mm.




